Macro Impacts

### 2016-08-05 Macro Impacts Revised.tex
Removed unnecessary section
update

E&\approx\f{\lambda+2\mu}{K^2}\f{p_0^2h\pi^3r_X^4}{\lambda_0^2}\,,\\

@@

E&\approx\f{\lambda+2\mu}{K^2}\f{h p_0^2\pi^3\Delta r^2(3r_0+2\Delta r)^2}{9\lambda_0^2}

@@

@@

\section{New Calculation}
Instead of the hypergeometric function, whose form is unnecessarily linked to the profile of the pressure wave, suppose the pressure wave has the Fourier transform

@@

\f{4\pi p_0}{k\cos\theta}\sin\p{\f{h k\cos\theta}{2}}F(b k\sin\theta)

@@

and write

@@

F^2 = \sum_{i = 0}^\infty G_i \times (bk\sin\theta)^i\,.

@@

The term $e^{-k\f{Q}{T}}$ tells us at what point we can stop the integral.

>>>>

E_{\te{propagated}}&\approx\f{\lambda+2\mu}{K^2}\f{p_0^2h\pi^3r_X^4}{\lambda_0^2}\,,\\

@@

E_{\te{propagated}}&\approx\f{\lambda+2\mu}{K^2}\f{h p_0^2\pi^3\Delta r^2(3r_0+2\Delta r)^2}{9\lambda_0^2}

@@

The total energy of this general pressure wave is
E_{\te{total}} = 2\pi p_0^2h\f{\lambda+2\mu}{K^2}\int_0^\infty r\diff r f(r)^2\,.
Hence, in general
\Xi = \f{2\pi^2}{\lambda_0^2}\f{(b^2 f_1(b)-a^2f_1(a))^2}{\int_0^\infty r\diff r f(r)^2}

@@

\section{A Good Method of Overestimation}
Forget about the hypergeometric. Take the $f$ source to be of the optimal form to produce seismic waves that will reach the detector, i.e. take $f= A\delta(k-k_0)$ where $k_0$ is the lowest frequency of response of the moon seismometers. In this case, the total energy of the ray just goes as $e^{-k_0\f{T_{m,n}}{Q_{m,n}}}$. According to http://nssdc.gsfc.nasa.gov/nmc/experimentDisplay.do?id=1971-008C-04, the lowest useful range of any of the lunar seismometers (some had higher) was $0.004\te{Hz}$. The velocity of p-waves near the surface is $1\te{km\,s}^{-1}$, and so this corresponds to $k_0 = 2\pi\times 0.004\te{km}^{-1}$. However, another useful quantity may be the peak response, which is $0.45\te{Hz}$. I'll run the model with both of these quantities.
\section{What Counts as Detectable?}
The most sensitive of the moon seismometers could measure $0.008\te{mgal}=8\times 10^{-8}\te{m\,s}^{-2}$. Their mass is approximately $10\te{kg}$, and they are sensitive to displacements down to $0.3\times 10^{-9}\te{m}$. If in a HEALPix pixel, the energy density is $\epsilon$, the energy on the seismometer is given by the surface area the seismometer occupies. It's radius is $11.5\te{cm}$. Call the radius $r_s$, the displacement sensitivity $D$, the mass of the seismometer $M$, and the acceleration sensitivity $A$. Then the seismometer will sense $\epsilon$ such that

@@

\epsilon\f{\pi r_s^2}{MD} \geq A

@@

i.e.

@@

\epsilon \geq 6\times 10^{-9} \te{J\,km}^{-2}\,.

@@
